\thetitle

### 2020-11-21 writing/mutate.tex
working on last bit of results

\begin{figure*}
  \centering
  \includegraphics[scale=0.35]{./plots/mutant-breakdown}
  \caption{Interesting debugging scenarios produced by our mutators. Counts are cut off at 50.}
  \label{fig:mutant-breakdown}
\end{figure*}

With the definition of interesting debugging scenarios in hand, we analyze how effective our mutators
are for turning the benchmarks into interesting debugging scenarios.
Indeed the mutators produce at least 72192 interesting debugging scenarios
across all mutants --- there are potentially many more but this is how
many we examined. 
Figure~\ref{fig:mutant-breakdown} breaks down the interesting
debugging scenarios produced  for each benchmark by mutator 
but counts are cut off at 50. The mutators produce at least 40 interesting
scenarios for every benchmark, and these scenarios originate from at
least four different mutators per benchmark.  Thus the mutators result in 
a sizeable and diverse population of scenarios for every benchmark.
Furthermore, every mutator contributes scenarios to at least one
benchmark. Especially some mutators  target specific features of
benchmarks, which
justifies their inclusion. For
instance the class-focused mutators are effective in \texttt{take5}
which jives with the fact that it is the benchmark with 
the most extensive use of object-oriented features.

>>>>

%\begin{figure*}
%  \centering
%  \includegraphics[scale=0.35]{./plots/mutant-breakdown}
%  \caption{Interesting debugging scenarios produced by our mutators. Counts are cut off at 50.}
%  \label{fig:mutant-breakdown}
%\end{figure*}

With the definition of interesting debugging scenarios in hand, we analyze how effective our mutators
are for turning the benchmarks into interesting debugging scenarios.
Indeed the mutators produce at least 72192 interesting debugging scenarios
across all mutants --- there are potentially many more but this is how
many we examined. In more detail, the mutators produce at least 40 interesting
scenarios for every benchmark, and these scenarios originate from at
least four different mutators per benchmark.  Thus the mutators result in 
a sizeable and diverse population of scenarios for every benchmark.
Furthermore, every mutator contributes scenarios to at least one
benchmark. Especially some mutators  target specific features of
benchmarks even if they do not contribute interesting scenarios to other
benchmarks, which
justifies their inclusion. For
instance the class-focused mutators are effective in \texttt{take5}
which jives with the fact that it is the benchmark with 
the most extensive use of object-oriented features.

### 2020-11-21 writing/results.tex
working on last bit of results

Figure~\ref{fig:effort-table} shows the distribution of programmer effort
for the sampled interesting debugging --- in contrast to the usefulness
comparisons these results do not generalize to the full population.

>>>>

Figure~\ref{fig:effort-table} shows the distribution of programmer effort
for  the sampled interesting debugging scenarios . Unlike the usefulness
comparisons above, these results do not generalize to the full population.
Still, as we discuss in section~\ref{subsec:effort}, they provide an
alternative view of the workings of the rational programmer. There are two
immediate take-aways from the figure. First, the effort for succesfully
debugging interesting scenarios (in green) for the random mode of the
rational program  follows  a normal distribution as expected.\footnote{The
random mode distribution is indistinguishable for all three semantics and thus the figure~\ref{fig:effort-table} 
only shows one plot.} In contrast, in the other modes, succesful effort coalesces at
the left side of the plot, meaning that in most cases the programmer needs
to type a single component to debug a scenario. Even in the minority of
cases where the blame or exception rational programmer has to work harder, the number of
modules that that need to be typed is small relative to the random
rational programmer. A second point of interest is that the exceptions of
the erasure semantics either help the rational programmer immediately or 
the rational programmer fails to debug a scenario (in red). This shouldn't
come as a surprise; no matter how many type annotations the programmer
adds to an erasure program, if the program
